### 2020-07-25 10_prb_resubmission_01/01_supplementary/supplementary.tex
Generated new arxiv submission

%\documentclass[aps,prb,amsmath,twocolumn,amssymb,titlepage]{revtex4-1}
\documentclass[10pt]{revtex4-1}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{nicefrac}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsmath} 
\usepackage{subfigure}
\usepackage{multirow} 
\usepackage{tabularx} 
\usepackage{array}
\usepackage{units}
\usepackage{tensor} 
\usepackage{braket}
\usepackage{bm}
\usepackage{hyperref}
\usepackage[resetlabels, labeled]{multibib}
\usepackage{xcolor}
\usepackage{bbm}
\usepackage{xfp}
\usepackage[labelfont=bf,textfont=md,justification=raggedright,font=footnotesize]{caption}
\usepackage{booktabs}
\renewcommand{\figurename}{Figure}
\renewcommand{\tablename}{Table}
\renewcommand{\thetable}{\arabic{table}}
%\captionsetup{justification=raggedright, singlelinecheck = false}
%\usepackage{makecell}
%\usepackage{cellspace}

%\newcites{supp}{References}

%\def\basiceval#1{\the\numexpr#1\relax}

@@

\newcommand{\hc}{^{\dagger}}
\newcommand{\ad}{\operatorname{{\mathrm ad}}}
\newcommand{\adn}{\ad_{\hat n}}
\newcommand{\adx}{\ad_{\hat x}}
\newcommand{\adX}[1][]{\ad_{\hat {\mathbf{X}}_{#1}}}
\newcommand{\adp}{\ad_{\hat p}}
\newcommand{\calD}{\mathcal{D}}    %Caligraphic D
\newcommand{\inbk}[1]{\left[ #1 \right]}
\newcommand{\inbr}[1]{\left\{ #1 \right\}}
\newcommand{\inp}[1]{\left( #1 \right)}
\newcommand{\pd}{\partial}
\newcommand{\pdf}[3]{\frac{\pd^{#1} #2}{\pd #3^{#1}}} %Partial derivative
\newcommand{\fdf}[3][]{\frac{\delta^{#1} #2}{\delta #3^{#1}}} %Functional derivative

%ssh1

%Our test set in this experiment contained 1005 Hamiltonians (approx. 15.3\% of all data). Of the remaining 5556 Hamiltonians, 556 were %randomly assigned to the training set (approx. 8.5\%) and 5000 (approx. 76.2\%) were used to compute validation scores at each iteration. %These proportions between training and validation sets are such that approximately 10\%  of Hamiltonians from outside of the test set were %used for training at each iteration. The composition of the train + validation set for this experiment was 50.8\% of Hamiltonians with %winding number $W$ = 0 and 49.2\% with winding number $W$ = 1. The composition of the test set was 44.8\% of Hamiltonians with winding number %$W$ = 0 and 55.2\% with winding number $W=1$. \textcolor{blue}{Our learning algorithm of choice for this experiment was a simple decision %tree model \cite{breiman2017classification}}.\citequote{eigenvector_ensembling_alg}

%\documentclass{article}
%\usepackage{xfp}

%\begin{document}

%\fpeval{31/45}

%\fpeval{round(31/45,5)}

%\end{document}
\newcommand{\indicator}[1]{\mathbbm{1}_{\mathcal{#1}}}
%%%%%% Numerical experiments parameters
\newcommand\nPrec{2}    % precision digits
\newcommand\accPrec{4}  % precision digits for accuracy scores
\newcommand\nHam{6561}  % total number of hamiltonians
\newcommand\epsilonValue{0.01}  % epsilon criterium for test set
\newcommand\nExp{100}   % number of experiments
%%%table commands
%\newcommand{\tableRow}[1]{\\[#1 cm]\hline} %deprecated table row, but might be useful
\newcommand{\tableRow}[1]{\\[#1 cm]}
\newcommand{\tableRowHeader}[1]{\\[#1 cm]\hline}
\newcommand\tableRowHeaderEnd{\tableRowHeader{0.3}}
\newcommand\tableRowEnd{\tableRow{0.15}}
%\newcommand\SSHSys{\thead{SSH systems}}         deprecated, might be useful
%\newcommand\Feat{\thead{Features}}              deprecated, might be useful
%\newcommand\ValEig{\thead{Val. eigenvectors}}   deprecated, might be useful
%\newcommand\TestEig{\thead{Test eigenvectors}}  deprecated, might be useful
%\newcommand\ValHam{\thead{Val. Hamiltonians}}   deprecated, might be useful
%\newcommand\TestHam{\thead{Test Hamiltonians}}  deprecated, might be useful
\newcommand\SSHSys{SSH system}         
\newcommand\Feat{Features}              
\newcommand\ValEig{Val. eigenvectors}   
\newcommand\TestEig{Test eigenvectors}  
\newcommand\ValHam{Val. Hamiltonians}   
\newcommand\TestHam{Test Hamiltonians}

%%%%%%%%%%%%%%% ssh1 experiments
%%% data statistics
\newcommand\sshOneTrainNHam{556}
\newcommand\sshOneTrainFracHam{\fpeval{round(\sshOneTrainNHam/\nHam*100,\nPrec)}}
\newcommand\sshOneValNHam{5000}
\newcommand\sshOneValFracHam{\fpeval{round(\sshOneValNHam/\nHam*100,\nPrec)}}
\newcommand\sshOneTrainPlusValNHam{\fpeval{\sshOneTrainNHam+\sshOneValNHam}}
\newcommand\sshOneTestNHam{1005}
\newcommand\sshOneTestFracHam{\fpeval{round(\sshOneTestNHam/\nHam*100,\nPrec)}}
\newcommand\sshOneTrainPlusValWindZeroNHam{2822} %number of winding = 0 in train+val set
\newcommand\sshOneTrainPlusValWindZeroFracHam{\fpeval{round(\sshOneTrainPlusValWindZeroNHam/(\sshOneTrainNHam+\sshOneValNHam)*100,\nPrec)}}
\newcommand\sshOneTrainPlusValWindOneNHam{2734}  %number of winding = 1 in train+val set
\newcommand\sshOneTrainPlusValWindOneFracHam{\fpeval{round(\sshOneTrainPlusValWindOneNHam/(\sshOneTrainNHam+\sshOneValNHam)*100,\nPrec)}}
\newcommand\sshOneTestWindZeroNHam{378}      %number of winding = 0 in test set
\newcommand\sshOneTestWindOneNHam{466}       %number of winding = 1 in test set
\newcommand\sshOneTestWindZeroFracHam{\fpeval{round(\sshOneTestWindZeroNHam/(\sshOneTestWindZeroNHam+\sshOneTestWindOneNHam)*100,\nPrec)}}
\newcommand\sshOneTestWindOneFracHam{\fpeval{round(\sshOneTestWindOneNHam/(\sshOneTestWindZeroNHam+\sshOneTestWindOneNHam)*100,\nPrec)}}
%%% real space accuracies
%\newcommand\sshOneEigenTrainAcc{0.981438129496403}       % eigenvector training accuracy
%\newcommand\sshOneEigenValAcc{0.96392276}         % eigenvector val accuracy
%\newcommand\sshOneEigenTestAcc{0.78966836492891}        % eigenvector test accuracy
%\newcommand\sshOneHamTrainAcc{1.0}             % Hamiltonian training accuracy
%\newcommand\sshOneHamValAcc{1.0}               % Hamiltonian val accuracy
%\newcommand\sshOneHamTestAcc{0.9918720379146919}          % Hamiltonian test accuracy
%\newcommand\sshOneHamTestBaseline{\fpeval{round(\sshOneTestWindOneNHam/(\sshOneTestWindZeroNHam+\sshOneTestWindOneNHam),\accPrec)}}

%%% ssh1 baseline accuracy
\newcommand\sshOneHamTestBaseline{\fpeval{round(\sshOneTestWindOneNHam/(\sshOneTestWindZeroNHam+\sshOneTestWindOneNHam),\accPrec)}}
%%% x1 features table entries 
\newcommand\xOne{$X_1$}
\newcommand\xOneEigTrain{\fpeval{round(0.981438129496403,\accPrec)}}
\newcommand\xOneEigVal{\fpeval{round(0.96392276,\accPrec)}}
\newcommand\xOneEigTest{\fpeval{round(0.78966836492891,\accPrec)}}
\newcommand\xOneHamTrain{\fpeval{round(1.0,\accPrec)}}
\newcommand\xOneHamVal{\fpeval{round(1.0,\accPrec)}}
\newcommand\xOneHamTest{\fpeval{round(0.9918720379146919,\accPrec)}}
%%% x_S1 features table entries  
\newcommand\xSOne{$X_{\mathcal{S}_1}$}
\newcommand\xSOneEigTrain{\fpeval{round(0.9699771582733813,\accPrec)}}
\newcommand\xSOneEigVal{\fpeval{round(0.9444134200000001,\accPrec)}}
\newcommand\xSOneEigTest{\fpeval{round(0.7763444312796207,\accPrec)}}
\newcommand\xSOneHamTrain{\fpeval{round(0.9880395683453237,\accPrec)}}
\newcommand\xSOneHamVal{\fpeval{round(0.9853300000000002,\accPrec)}}
\newcommand\xSOneHamTest{\fpeval{round(0.9904502369668248,\accPrec)}}
%%% x^c_1 features table entries  
\newcommand\xcOne{$\hat{X}^c_1$}
\newcommand\xcOneEigTrain{\fpeval{round(0.9753276978417266,\accPrec)}}
\newcommand\xcOneEigVal{\fpeval{round(0.9521145999999999,\accPrec)}}
\newcommand\xcOneEigTest{\fpeval{round(0.7373592417061612,\accPrec)}}
\newcommand\xcOneHamTrain{\fpeval{round(0.9982553956834532,\accPrec)}}
\newcommand\xcOneHamVal{\fpeval{round(0.9975820000000002,\accPrec)}}
\newcommand\xcOneHamTest{\fpeval{round(0.9916232227488153,\accPrec)}}
%%% x^cE_1 features table entries  
\newcommand\xcEOne{$\hat{X}^c_{\mathcal{E}_1}$}
\newcommand\xcEOneEigTrain{\fpeval{round(0.9755357913669066,\accPrec)}}
\newcommand\xcEOneEigVal{\fpeval{round(0.8280291200000001,\accPrec)}}
\newcommand\xcEOneEigTest{\fpeval{round(0.6066537914691943,\accPrec)}}
\newcommand\xcEOneHamTrain{\fpeval{round(0.998525179856115,\accPrec)}}
\newcommand\xcEOneHamVal{\fpeval{round(0.997906,\accPrec)}}
\newcommand\xcEOneHamTest{\fpeval{round(0.9190876777251185,\accPrec)}}
%%% x^cSE_1 features table entries  
\newcommand\xcSEOne{$\hat{X}^c_{\mathcal{S}_1,\mathcal{E}_1}$}
\newcommand\xcSEOneEigTrain{\fpeval{round(0.9701161870503597,\accPrec)}}
\newcommand\xcSEOneEigVal{\fpeval{round(0.9444223399999998,\accPrec)}}
\newcommand\xcSEOneEigTest{\fpeval{round(0.8176174170616113,\accPrec)}}
\newcommand\xcSEOneHamTrain{\fpeval{round(0.9882014388489206,\accPrec)}}
\newcommand\xcSEOneHamVal{\fpeval{round(0.9853120000000001,\accPrec)}}
\newcommand\xcSEOneHamTest{\fpeval{round(0.9933530805687205,\accPrec)}}
%%% x^s_1 features table entries  
\newcommand\xsOne{$\hat{X}^s_1$}
\newcommand\xsOneEigTrain{\fpeval{round(0.9751985611510792,\accPrec)}}
\newcommand\xsOneEigVal{\fpeval{round(0.9533083600000001,\accPrec)}}
\newcommand\xsOneEigTest{\fpeval{round(0.7313738151658769,\accPrec)}}
\newcommand\xsOneHamTrain{\fpeval{round(0.9930935251798562,\accPrec)}}
\newcommand\xsOneHamVal{\fpeval{round(0.9905759999999999,\accPrec)}}
\newcommand\xsOneHamTest{\fpeval{round(0.9855568720379146,\accPrec)}}
%%% x^SO_1 features table entries  
\newcommand\xsOOne{$\hat{X}^s_{\mathcal{O}_1}$}
\newcommand\xsOOneEigTrain{\fpeval{round(0.807853597122302,\accPrec)}}
\newcommand\xsOOneEigVal{\fpeval{round(0.6941595600000001,\accPrec)}}
\newcommand\xsOOneEigTest{\fpeval{round(0.5419954976303317,\accPrec)}}
\newcommand\xsOOneHamTrain{\fpeval{round(0.9919424460431654,\accPrec)}}
\newcommand\xsOOneHamVal{\fpeval{round(0.7088179999999998,\accPrec)}}
\newcommand\xsOOneHamTest{\fpeval{round(0.4797630331753555,\accPrec)}}
%%% x^SSO_1 features table entries  
\newcommand\xsSOOne{$\hat{X}^s_{\mathcal{S}_1,\mathcal{O}_1}$}
\newcommand\xsSOOneEigTrain{\fpeval{round(0.96949190647482,\accPrec)}}
\newcommand\xsSOOneEigVal{\fpeval{round(0.9456364800000001,\accPrec)}}
\newcommand\xsSOOneEigTest{\fpeval{round(0.7818372037914694,\accPrec)}}
\newcommand\xsSOOneHamTrain{\fpeval{round(0.9875539568345324,\accPrec)}}
\newcommand\xsSOOneHamVal{\fpeval{round(0.9853839999999998,\accPrec)}}
\newcommand\xsSOOneHamTest{\fpeval{round(0.9398933649289098,\accPrec)}}

%ssh2
\newcommand\sshTwoTrainNHam{2761}
\newcommand\sshTwoTrainFracHam{\fpeval{round(\sshTwoTrainNHam/\nHam*100,\nPrec)}}
\newcommand\sshTwoValNHam{2760}
\newcommand\sshTwoValFracHam{\fpeval{round(\sshTwoValNHam/\nHam*100,\nPrec)}}
\newcommand\sshTwoTrainPlusValNHam{\fpeval{\sshTwoTrainNHam+\sshTwoValNHam}}
\newcommand\sshTwoTestNHam{1040}
\newcommand\sshTwoTestFracHam{\fpeval{round(\sshTwoTestNHam/\nHam*100,\nPrec)}}

\newcommand\sshTwoTrainPlusValWindMinusOneNHam{988} %number of winding = -1 in train+val set
\newcommand\sshTwoTrainPlusValWindMinusOneFracHam{\fpeval{round(\sshTwoTrainPlusValWindMinusOneNHam/\sshTwoTrainPlusValNHam*100,\nPrec)}}
\newcommand\sshTwoTrainPlusValWindZeroNHam{1795} %number of winding = 0 in train+val set
\newcommand\sshTwoTrainPlusValWindZeroFracHam{\fpeval{round(\sshTwoTrainPlusValWindZeroNHam/\sshTwoTrainPlusValNHam*100,\nPrec)}}
\newcommand\sshTwoTrainPlusValWindOneNHam{1781}  %number of winding = 1 in train+val set
\newcommand\sshTwoTrainPlusValWindOneFracHam{\fpeval{round(\sshTwoTrainPlusValWindOneNHam/\sshTwoTrainPlusValNHam*100,\nPrec)}}
\newcommand\sshTwoTrainPlusValWindTwoNHam{957}   %number of winding = 2 in train+val set
\newcommand\sshTwoTrainPlusValWindTwoFracHam{\fpeval{round(\sshTwoTrainPlusValWindTwoNHam/\sshTwoTrainPlusValNHam*100,\nPrec)}}

\newcommand\sshTwoTestWindMinusOneNHam{312} %number of winding = -1 in test set
\newcommand\sshTwoTestWindZeroNHam{95} %number of winding = 0 in test set
\newcommand\sshTwoTestWindOneNHam{109}  %number of winding = 1 in test set
\newcommand\sshTwoTestWindTwoNHam{343}   %number of winding = 2 in test set 
\newcommand\sshTwoTestWindMinusOneFracHam{\fpeval{round(\sshTwoTestWindMinusOneNHam/(\sshTwoTestWindMinusOneNHam+\sshTwoTestWindZeroNHam+\sshTwoTestWindOneNHam+\sshTwoTestWindTwoNHam)*100,\nPrec)}}
\newcommand\sshTwoTestWindZeroFracHam{\fpeval{round(\sshTwoTestWindZeroNHam/(\sshTwoTestWindMinusOneNHam+\sshTwoTestWindZeroNHam+\sshTwoTestWindOneNHam+\sshTwoTestWindTwoNHam)*100,\nPrec)}}
\newcommand\sshTwoTestWindOneFracHam{\fpeval{round(\sshTwoTestWindOneNHam/(\sshTwoTestWindMinusOneNHam+\sshTwoTestWindZeroNHam+\sshTwoTestWindOneNHam+\sshTwoTestWindTwoNHam)*100,\nPrec)}}
\newcommand\sshTwoTestWindTwoFracHam{\fpeval{round(\sshTwoTestWindTwoNHam/(\sshTwoTestWindMinusOneNHam+\sshTwoTestWindZeroNHam+\sshTwoTestWindOneNHam+\sshTwoTestWindTwoNHam)*100,\nPrec)}}

\newcommand\sshTwoEigenTrainAcc{0.999655849329953}       % eigenvector training accuracy
\newcommand\sshTwoEigenValAcc{0.9708922101449275}         % eigenvector val accuracy
\newcommand\sshTwoEigenTestAcc{0.6634109429569267}        % eigenvector test accuracy
\newcommand\sshTwoHamTrainAcc{1.0}             % Hamiltonian training accuracy
\newcommand\sshTwoHamValAcc{0.9972499999999997}               % Hamiltonian val accuracy
\newcommand\sshTwoHamTestAcc{0.879697322467986}          % Hamiltonian test accuracy

%%% ssh2 baseline accuracy
\newcommand\sshTwoHamTestBaseline{\fpeval{round(\sshTwoTestWindTwoNHam/(\sshTwoTestWindMinusOneNHam+\sshTwoTestWindZeroNHam+\sshTwoTestWindOneNHam+\sshTwoTestWindTwoNHam),\accPrec)}}
%%% x2 features table entries 
\newcommand\xTwo{$X_2$}
\newcommand\xTwoEigTrain{\fpeval{round(0.999655849329953,\accPrec)}}
\newcommand\xTwoEigVal{\fpeval{round(0.9708922101449275,\accPrec)}}
\newcommand\xTwoEigTest{\fpeval{round(0.6634109429569267,\accPrec)}}
\newcommand\xTwoHamTrain{\fpeval{round(1.0,\accPrec)}}
\newcommand\xTwoHamVal{\fpeval{round(0.9972499999999997,\accPrec)}}
\newcommand\xTwoHamTest{\fpeval{round(0.879697322467986,\accPrec)}}

%%% x_S2 features table entries  
\newcommand\xSTwo{$X_{\mathcal{S}_2}$}
\newcommand\xSTwoEigTrain{\fpeval{round(0.9996107207533504,\accPrec)}}
\newcommand\xSTwoEigVal{\fpeval{round(0.9589830072463768,\accPrec)}}
\newcommand\xSTwoEigTest{\fpeval{round(0.6168351571594877,\accPrec)}}
\newcommand\xSTwoHamTrain{\fpeval{round(1.0,\accPrec)}}
\newcommand\xSTwoHamVal{\fpeval{round(0.9961050724637681,\accPrec)}}
\newcommand\xSTwoHamTest{\fpeval{round(0.8625611175785797,\accPrec)}}
%%% x^c_2 features table entries  
\newcommand\xcTwo{$\hat{X}^c_2$}
\newcommand\xcTwoEigTrain{\fpeval{round(0.9996471930459978,\accPrec)}}
\newcommand\xcTwoEigVal{\fpeval{round(0.9740357971014493,\accPrec)}}
\newcommand\xcTwoEigTest{\fpeval{round(0.6895051222351573,\accPrec)}}
\newcommand\xcTwoHamTrain{\fpeval{round(1.0,\accPrec)}}
\newcommand\xcTwoHamVal{\fpeval{round(0.9976050724637681,\accPrec)}}
\newcommand\xcTwoHamTest{\fpeval{round(0.8862281722933641,\accPrec)}}
%%% x^cE_2 features table entries  
\newcommand\xcETwo{$\hat{X}^c_{\mathcal{E}_2}$}
\newcommand\xcETwoEigTrain{\fpeval{round(0.99943379210431,\accPrec)}}
\newcommand\xcETwoEigVal{\fpeval{round(0.8989626449275362,\accPrec)}}
\newcommand\xcETwoEigTest{\fpeval{round(0.5356883585564609,\accPrec)}}
\newcommand\xcETwoHamTrain{\fpeval{round(1.0,\accPrec)}}
\newcommand\xcETwoHamVal{\fpeval{round(0.9954927536231883,\accPrec)}}
\newcommand\xcETwoHamTest{\fpeval{round(0.7896856810244468,\accPrec)}}

%%% x^cSE_2 features table entries  
\newcommand\xcSETwo{$\hat{X}^c_{\mathcal{S}_2,\mathcal{E}_2}$}
\newcommand\xcSETwoEigTrain{\fpeval{round(0.9994432452010141,\accPrec)}}
\newcommand\xcSETwoEigVal{\fpeval{round(0.8998827173913044,\accPrec)}}
\newcommand\xcSETwoEigTest{\fpeval{round(0.5029968568102445,\accPrec)}}
\newcommand\xcSETwoHamTrain{\fpeval{round(1.0,\accPrec)}}
\newcommand\xcSETwoHamVal{\fpeval{round(0.9956086956521739,\accPrec)}}
\newcommand\xcSETwoHamTest{\fpeval{round(0.7670896391152502,\accPrec)}}
%%% x^s_2 features table entries  
\newcommand\xsTwo{$\hat{X}^s_2$}
\newcommand\xsTwoEigTrain{\fpeval{round(0.9996523723288662,\accPrec)}}
\newcommand\xsTwoEigVal{\fpeval{round(0.9735059057971014,\accPrec)}}
\newcommand\xsTwoEigTest{\fpeval{round(0.6878407450523867,\accPrec)}}
\newcommand\xsTwoHamTrain{\fpeval{round(1.0,\accPrec)}}
\newcommand\xsTwoHamVal{\fpeval{round(0.9970652173913043,\accPrec)}}
\newcommand\xsTwoHamTest{\fpeval{round(0.8898835855646101,\accPrec)}}
%%% x^SO_2 features table entries  
\newcommand\xsOTwo{$\hat{X}^s_{\mathcal{O}_2}$}
\newcommand\xsOTwoEigTrain{\fpeval{round(0.9994471206084752,\accPrec)}}
\newcommand\xsOTwoEigVal{\fpeval{round(0.9042001086956524,\accPrec)}}
\newcommand\xsOTwoEigTest{\fpeval{round(0.552662980209546,\accPrec)}}
\newcommand\xsOTwoHamTrain{\fpeval{round(1.0,\accPrec)}}
\newcommand\xsOTwoHamVal{\fpeval{round(0.9917789855072465,\accPrec)}}
\newcommand\xsOTwoHamTest{\fpeval{round(0.7427124563445866,\accPrec)}}
%%% x^SSO_2 features table entries  
\newcommand\xsSOTwo{$\hat{X}^s_{\mathcal{S}_2,\mathcal{O}_2}$}
\newcommand\xsSOTwoEigTrain{\fpeval{round(0.9992071713147413,\accPrec)}}
\newcommand\xsSOTwoEigVal{\fpeval{round(0.8203919927536232,\accPrec)}}
\newcommand\xsSOTwoEigTest{\fpeval{round(0.41268987194412105,\accPrec)}}
\newcommand\xsSOTwoHamTrain{\fpeval{round(1.0,\accPrec)}}
\newcommand\xsSOTwoHamVal{\fpeval{round(0.9941884057971013,\accPrec)}}
\newcommand\xsSOTwoHamTest{\fpeval{round(0.5903026775320139,\accPrec)}}

%%% more feature commands
%\newcommand\xcSE{$\hat{X}^c_{\mathcal{S},\mathcal{E}}$}
%\newcommand\xsSO{$\hat{X}^s_{\mathcal{S},\mathcal{O}}$}

\newcommand\xalpha{$X_\alpha$}
\newcommand\xSalpha{$X_{\mathcal{S}_\alpha}$}

\newcommand\xcalpha{$\hat{X}^c_\alpha$}
\newcommand\xcEalpha{$\hat{X}^c_{\mathcal{E}_\alpha}$}
\newcommand\xcSEalpha{$\hat{X}^c_{\mathcal{S}_\alpha,\mathcal{E}_\alpha}$}

\newcommand\xsalpha{$\hat{X}^s_\alpha$}
\newcommand\xsOalpha{$\hat{X}^s_{\mathcal{O}_\alpha}$}
\newcommand\xsSOalpha{$\hat{X}^s_{\mathcal{S}_\alpha,\mathcal{O}_\alpha}$}

\newcommand\nEst{25}   % number of estimators in random forest

\newcounter{quoter}
\setcounter{quoter}{0}
\renewcommand*{\thequoter}{%
  %\textbf{%
  %  \ifnum\value{custom}<1000 0\fi
  %  \ifnum\value{custom}<100 0\fi
  %  \ifnum\value{custom}<10 0\fi
  %  \arabic{custom}%
  \textbf{[\arabic{quoter}]}
  }%

\newcommand{\genquote}[1]{\refstepcounter{quoter} \label{#1} \ref{#1}}
\newcommand{\citequote}[1]{\ref{#1}}

>>>>

%\documentclass[aps,prb,amsmath,twocolumn,amssymb,titlepage]{revtex4-1}
\documentclass[10pt]{revtex4-1}
\usepackage{graphicx}
\usepackage{nicefrac}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsmath} 
\usepackage{subfigure}
\usepackage{multirow} 
\usepackage{tabularx} 
\usepackage{array}
\usepackage{units}
\usepackage{tensor} 
\usepackage{braket}
\usepackage{bm}
\usepackage{hyperref}
\usepackage[resetlabels, labeled]{multibib}
%\newcites{supp}{References}

@@

\newcommand{\hc}{^{\dagger}}
\newcommand{\ad}{\operatorname{{\mathrm ad}}}
\newcommand{\adn}{\ad_{\hat n}}
\newcommand{\adx}{\ad_{\hat x}}
\newcommand{\adX}[1][]{\ad_{\hat {\mathbf{X}}_{#1}}}
\newcommand{\adp}{\ad_{\hat p}}
\newcommand{\calD}{\mathcal{D}}    %Caligraphic D
\newcommand{\inbk}[1]{\left[ #1 \right]}
\newcommand{\inbr}[1]{\left\{ #1 \right\}}
\newcommand{\inp}[1]{\left( #1 \right)}
\newcommand{\pd}{\partial}
\newcommand{\pdf}[3]{\frac{\pd^{#1} #2}{\pd #3^{#1}}} %Partial derivative
\newcommand{\fdf}[3][]{\frac{\delta^{#1} #2}{\delta #3^{#1}}} %Functional
                                %derivative

\newcommand\xSOne{$X_{\mathcal{S}_1}$}
\newcommand\xcSEOne{$\hat{X}^c_{\mathcal{S}_1,\mathcal{E}_1}$}
\newcommand\xsSOOne{$\hat{X}^s_{\mathcal{S}_1,\mathcal{O}_1}$}
\newcommand\xSTwo{$X_{\mathcal{S}_2}$}
\newcommand\xcSETwo{$\hat{X}^c_{\mathcal{S}_2,\mathcal{E}_2}$}
\newcommand\xsSOTwo{$\hat{X}^s_{\mathcal{S}_2,\mathcal{O}_2}$}

\begin{document}
\nocite{*}

\begin{figure}
  \centering
  \includegraphics[width=.37\textwidth]{./ssh/ssh_model.pdf}
  \caption{Schematic set-up of a 1D SSH system. Here $t_1$ and $t_2$ are nearest-neighbor hoppings while $T_1$ and $T_2$ are second nearest-neighbor hoppings.}
\label{fig:model}
\end{figure}

\begin{figure}%[h!]
  \centering
  \includegraphics[width=.37\textwidth]{./ssh/winding.png}
  \caption{Winding number. The winding number of a closed, oriented curve with respect to a reference point is a topological invariant that counts how many times the curve winds around the point. Picture credits: Jim Belk, public domain.}
\label{fig:winding}
\end{figure}

\begin{figure}
\centering
\subfigure[]{\label{eng_feat_ssh1:a}\includegraphics[width=.32\textwidth]{./supp_figures/ssh1/periodic_100_6561/real_space_best_04_sites/merge_imshow_winding_grids_second_sim.png}}
\subfigure[]{\label{eng_feat_ssh1:b}\includegraphics[width=.32\textwidth]{./supp_figures/ssh1/periodic_100_6561/dct_best_04_wavevector_sites_from_best_04_real_space_sites/merge_imshow_winding_grids_second_sim.png}}
\subfigure[]{\label{eng_feat_ssh1:c}\includegraphics[width=.32\textwidth]{./supp_figures/ssh1/periodic_100_6561/dst_best_04_wavevector_sites_from_best_04_real_space_sites/merge_imshow_winding_grids_second_sim.png}}
\caption{Phase diagrams learned from compressed representations of the SSH 1 system. (a) Phase diagram learned using the real space features \xSOne.  (b) Phase diagram learned from the DCT topological features \xcSEOne. (b) Phase diagram learned from the DST topological features \xsSOOne.}
\label{eng_feat_ssh1}
\end{figure}

\begin{figure}
\centering
\subfigure[]{\label{eng_feat_ssh2:a}\includegraphics[width=.32\textwidth]{./supp_figures/ssh2/periodic_100_6561/real_space_best_12_sites/merge_imshow_winding_grids_sim.png}}
\subfigure[]{\label{eng_feat_ssh2:b}\includegraphics[width=.32\textwidth]{./supp_figures/ssh2/periodic_100_6561/dct_best_12_wavevector_sites_from_best_12_real_space_sites/merge_imshow_winding_grids_sim.png}}
\subfigure[]{\label{eng_feat_ssh2:c}\includegraphics[width=.32\textwidth]{./supp_figures/ssh2/periodic_100_6561/dst_best_12_wavevector_sites_from_best_12_real_space_sites/merge_imshow_winding_grids_sim.png}}
\caption{Phase diagrams learned from compressed representations of the SSH 2 system. (a) Phase diagram learned using the real space features \xSTwo.  (b) Phase diagram learned from the DCT topological features \xcSETwo. (b) Phase diagram learned from the DST topological features \xsSOTwo.}
\label{eng_feat_ssh2}
\end{figure}

\begin{figure}
\centering
\subfigure[]{\label{feature_importances_ssh1_140}\includegraphics[width=.32\textwidth]{./supp_figures/ssh1/periodic_140_6561/plot_feature_importances.png}}
\subfigure[]{\label{feature_importances_ssh1_180}\includegraphics[width=.32\textwidth]{./supp_figures/ssh1/periodic_180_6561/plot_feature_importances.png}}
\subfigure[]{\label{feature_importances_ssh1_220}\includegraphics[width=.32\textwidth]{./supp_figures/ssh1/periodic_220_6561/plot_feature_importances.png}}
\caption{Information entropy signatures obtained for experiment 1 with higher lattice sizes. (a) Information entropy signature for 70 unit cells. (b) Information entropy signature for 90 unit cells. (c) Information entropy signature for 110 unit cells.}
\label{feature_importances_ssh1_longer_lattices}
\end{figure}
\begin{figure}
\centering
\subfigure[]{\label{feature_importances_ssh2_140}\includegraphics[width=.32\textwidth]{./supp_figures/ssh2/periodic_140_6561/plot_feature_importances.png}}
\subfigure[]{\label{feature_importances_ssh2_180}\includegraphics[width=.32\textwidth]{./supp_figures/ssh2/periodic_180_6561/plot_feature_importances.png}}
\subfigure[]{\label{feature_importances_ssh2_220}\includegraphics[width=.32\textwidth]{./supp_figures/ssh2/periodic_220_6561/plot_feature_importances.png}}
\caption{Information entropy signatures obtained for experiment 2 with higher lattice sizes. (a) Information entropy signature for 70 unit cells. (b) Information entropy signature for 90 unit cells. (c) Information entropy signature for 110 unit cells.}
\label{feature_importances_ssh2_longer_lattices}
\end{figure}

\begin{figure}
\centering
\subfigure[]{\label{cumulative_entropy_ssh1_140}\includegraphics[width=.32\textwidth]{./supp_figures/ssh1/periodic_140_6561/plot_cumulative_feature_importances}}
\subfigure[]{\label{cumulative_entropy_ssh1_180}\includegraphics[width=.32\textwidth]{./supp_figures/ssh1/periodic_180_6561/plot_cumulative_feature_importances}}
\subfigure[]{\label{cumulative_entropy_ssh1_220}\includegraphics[width=.32\textwidth]{./supp_figures/ssh1/periodic_220_6561/plot_cumulative_feature_importances}}
\caption{Cumulative entropy distributions for higher lattice sizes in experiment 1. (a) Cumulative entropy distribution for 70 unit cells. (b) Cumulative entropy distribution for 90 unit cells. (c) Cumulative entropy distribution for 110 unit cells.}
\label{cdf1}
\end{figure}

\begin{figure}
\centering
\subfigure[]{\label{cumulative_entropy_ssh2_140}\includegraphics[width=.32\textwidth]{./supp_figures/ssh2/periodic_140_6561/plot_cumulative_feature_importances}}
\subfigure[]{\label{cumulative_entropy_ssh2_180}\includegraphics[width=.32\textwidth]{./supp_figures/ssh2/periodic_180_6561/plot_cumulative_feature_importances}}
\subfigure[]{\label{cumulative_entropy_ssh2_220}\includegraphics[width=.32\textwidth]{./supp_figures/ssh2/periodic_220_6561/plot_cumulative_feature_importances}}
\caption{Cumulative entropy distributions for higher lattice sizes in experiment 2. (a) Cumulative entropy distributions for 70 unit cells. (b) Cumulative entropy distributions for 90 unit cells. (c) Cumulative entropy distributions for 110 unit cells.}
\label{cdf2}
\end{figure}

%\newpage
%\bibliographystylesupp{ieeetr}
%\bibliographysupp{supp}

%%%%%%%%%%%%%%%%% bibliography %%%%%%%%%%%%%%%%%%%%
\begin{thebibliography}{6}%
